\textls[-0]{\thetitle}

### 2023-03-22 casestudies.tex
Rephrase in a more qualitative style.

>>>>

% I think the following is a bit weird ... not enough quantative and not enough qualititive
% When programming in a direct style, before using FPOP, the STLC base module 
% will take around 350LOCs, and STLC with one feature is around 400 LOCs, because
% it requires to repeat the definition of the STLC base definition. It will take 
% more space when we add more features into STLC.

% After using FPOP, the 
% STLC base family also take about 350 LOCs. However, one feature as children family takes only about 100~250 LOCs. What's more, the mixin of two features usually only take 1~20 LOCs.
When programming in a direct style, before using FPOP, the STLC base module will take around 350 LOCs while using FPOP, the STLC base family takes about same amount of the code.

However, without FPOP, STLC with one feature will require around 400 LOCs as the definition of STLC base is repeated. On the other hand, using FPOP, each feature as extended family only requires ranging from 100~250 LOCs. What's more, without FPOP, STLC with multiple features will require more and more while using FPOP's mixin feature, tens of LOCs is enough.
